### 2022-03-01 manuscript.tex
save manuscript

>>>>

\section*{MakeDist}
The MakeDist function is applied function over an R dataframe and returns an 
object of class "UnivarMixingDistribution"

\subsection*{Usage}
MakeDist(df)

Variables of R dataframe to b used in making mixture distribution 
\begin{center}
    \begin{tabular}{ | l | p{4cm} | p{7cm} |}
    \hline
    Argument & Summary & Options \\ \hline
    dist & A string specifying a distribution family.  & “Beta”, “Cauchy”, 
    “Lnorm”, “Logis”, “Unif”, “Lst” (location scale t distribution), 
    “Weibull”, “Fd”, “Norm”,  “Chisq”, 
    “Gammad”, “Exp”
	 “Binom”, “Dirac”, “Pois”, “Hyper”, “Nbinom”, “Geom” \\ \hline
    param1 & A real number specifying the first parameter value of the 
    distribution. & Beta: shape1; 
	Cauchy: location; 
	Lnorm: meanlog; 
	Logis: location; 
	Unif: min; 
	Lst: location; 
	Weibull: shape;
	Fd: df1;
	Norm: mean;
	Chisq: df;
	Gammad: scale;
	Exp: rate; 
	Binom: size;
	Dirac: location;
	Pois: lambda;
	Hyper: m;
	Nbinom: n;
	Geom: prob
     \\ \hline
    param2 & A real number specifying the second parameter value of the 
    distribution. & Beta: shape2; 
	Cauchy: scale; 
	Lnorm: slog; 
	Logis: scale; 
	Unif: Max; 
	Lst: scale; 
	Weibull: scale; 
	Fd: df2; 
	Norm: sd; 
	Chisq: ncp; 
	Gammad: shape; 
	Binom: prob; 
	Hyper: n; 
	Nbinom: p \\
    \hline
    param3 & A real number specifying the third parameter value of the 
    distribution. & Lst: df;
	Hyper: k \\
	\hline
	weight & A real number between 0 and 1 specifying the weight given to the 
	distribution in the overall mixture distribution. The sum of the weight 
	column should equal 1. & ...
	\\
	\hline
    \end{tabular}
\end{center}

\newpage
% \begin{adjustwidth}{-3cm}{-1cm}
\begin{center}
% \caption{MakeDist parameter options}
    \begin{tabular}{ l l  p{2cm}  p{2cm}  p{2cm}}
    \hline
    \textbf{Distribution} & \textbf{dist} & \textbf{param1} & \textbf{param2} & 
    \textbf{param3} \newline \\ \hline
    Beta & Beta & shape1 & shape2 &  \\ 
    Cauch & Cauchy & location & scale &  \\
    Log-normal & Lnorm & meanlog & slog &  \\
    Logistic & Logis & location & scale &  \\
    Uniform & Unif & min & max &  \\
    Location Scale T & Lst & location & scale & df \\
    Weibull & Weibull & shape & scale &  \\
    F & Fd & df1 & df2 &  \\
    Normal & Norm & mean & sd &  \\
    Chisqure & Chisq & df &  &  \\
    Gamma & Gammad & scale & shape &  \\
    Exponential & Exp & rate &  &  \\
    Binomial & Binom & size & prob &  \\
    Dirac & Dirac & location &  &  \\
    Poisson & Pois & lambda &  &  \\
    Hypergeometric & Hyper & m & n & k \\
    Negative binomial & Nbinom & n & p &  \\
    Geometric & Geom & prob &  &  \\ \hline
    \end{tabular}
\end{center}
% \end{adjustwidth}
